Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-23 paper.qmd
Updated Figure 9

mse_scurve_b <- ggplot(error_scurve, 
                     aes(x = a1, 
                         y = MSE)) +
  geom_vline(xintercept = 0.10, linetype=2,
           color = "#bdbdbd", linewidth=1) +
  geom_vline(xintercept = 0.12,
             linetype="solid",
             color = "#bdbdbd",
             linewidth=1) +
  geom_vline(xintercept = 0.18, linetype=2,
             color = "#bdbdbd", linewidth=1) +
  geom_line(linewidth = 0.5) + 
  geom_point(size = 1) +
  scale_x_continuous(breaks = sort(unique(round(error_scurve$a1, 2)))[c(1, 3, 5, 6, 8, 10:12)]) +
  labs(x = expression(a[1]), y = "MSE") +
  ggtitle("(a)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5))

a1_m_scurve <- ggplot(error_scurve,
                     aes(x = a1,
                         y = b_non_empty)) +
  geom_point(size = 1) +
  geom_line(linewidth = 0.05) +
  geom_vline(xintercept = 0.116,
           linetype=2,
           color = "#bdbdbd",
           linewidth=1) +
  geom_hline(yintercept = 52,
           linetype=2,
           color = "#bdbdbd",
           linewidth=1) +
  # geom_vline(xintercept = 11, linetype="solid",
  #            color = "#bdbdbd", linewidth=1) +
  # geom_vline(xintercept = 9, linetype=2,
  #            color = "#bdbdbd", linewidth=1) +
  # geom_vline(xintercept = 13, linetype=2,
  #            color = "#bdbdbd", linewidth=1) +
  scale_y_continuous(breaks = sort(unique(error_scurve$b_non_empty))[-3]) +
  scale_x_continuous(breaks = sort(unique(round(error_scurve$a1, 2)))[c(1, 3, 5, 6, 8, 10:12)]) +
  labs(x = expression(a[1]), y = expression(m)) +
  ggtitle("(b)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 11),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12,
            angle=90),
        axis.ticks.x = element_line(linewidth = 0.5),
        axis.ticks.y = element_line(linewidth = 0.5),
        plot.title = element_text(size = 12),
        legend.title = element_text(size = 12),
        legend.text = element_text(size = 10),
        legend.key.height = unit(1, 'cm'),
        legend.key.width = unit(1, 'cm'),
        legend.key.size = unit(1, 'cm'))

@@

mse_scurve_lwd <- ggplot(error_rm_scurve, 
                     aes(x = mean_counts, 
                         y = MSE)) + 
  geom_point(
    size = 1
    ) +
  geom_line(
    linewidth = 0.3
    ) + 
  # geom_vline(xintercept = benchmark1, linetype="solid", 
  #            color = "#bdbdbd", linewidth=1, alpha = 0.5) +
  # scale_x_continuous("standardized bin count", 
  #        transform = "reverse") + 
  scale_x_continuous(breaks = unique(error_rm_scurve$mean_counts)) +
  xlab(expression(mean(n[h]))) +
  ylab("MSE") +
  ggtitle("(c)") +
  theme(aspect.ratio = 0.75,
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, 
            angle=90),
        plot.title = element_text(size = 12),
        axis.ticks.x = element_line(linewidth = 0.5),
        axis.ticks.y = element_line(linewidth = 0.5))

@@

distance_hist <- ggplot(
  distance_scurve, aes(x = distance)) +
    geom_histogram(
      aes(y = after_stat(count) / sum(after_stat(count))), 
      binwidth = bin_width) +
  scale_x_continuous(breaks = bin_labels, labels = round(bin_labels, 2)) +
  ylab("standardized number of edges") +
  xlab(expression(d^{(2)})) +
  ggtitle("(d)") +
  theme(aspect.ratio = 0.75,
        axis.title.x = element_text(size = 12),
        axis.title.y = element_text(size = 12, angle = 90),
        axis.text.x = element_text(size = 12),
        axis.text.y = element_text(size = 12),
        axis.ticks.x = element_line(), 
        plot.title = element_text(size = 12))

>>>>

mse_scurve_b <- ggplot(error_scurve, 
                     aes(x = a1, 
                         y = MSE)) +
  geom_vline(xintercept = 0.10, linetype=2,
           color = "#bdbdbd", linewidth=1) +
  geom_vline(xintercept = 0.12,
             linetype="solid",
             color = "#bdbdbd",
             linewidth=1) +
  geom_vline(xintercept = 0.18, linetype=2,
             color = "#bdbdbd", linewidth=1) +
  geom_line(linewidth = 0.5) + 
  geom_point(size = 1) +
  scale_x_continuous(breaks = sort(unique(round(error_scurve$a1, 2)))[c(1, 3, 5, 6, 8, 10:12)]) +
  labs(x = expression(a[1]), y = "MSE") +
  ggtitle("(a)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

a1_m_scurve <- ggplot(error_scurve,
                     aes(x = a1,
                         y = b_non_empty)) +
  geom_vline(xintercept = 0.12,
         linetype=2,
         color = "#bdbdbd",
         linewidth=1) +
  geom_hline(yintercept = 52,
           linetype=2,
           color = "#bdbdbd",
           linewidth=1) +
  geom_point(size = 1) +
  geom_line(linewidth = 0.05) +
  # geom_vline(xintercept = 11, linetype="solid",
  #            color = "#bdbdbd", linewidth=1) +
  # geom_vline(xintercept = 9, linetype=2,
  #            color = "#bdbdbd", linewidth=1) +
  # geom_vline(xintercept = 13, linetype=2,
  #            color = "#bdbdbd", linewidth=1) +
  scale_y_continuous(breaks = sort(unique(error_scurve$b_non_empty))[-3]) +
  scale_x_continuous(breaks = sort(unique(round(error_scurve$a1, 2)))[c(1, 3, 5, 6, 8, 10:12)]) +
  labs(x = expression(a[1]), y = expression(m)) +
  ggtitle("(b)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

@@

mse_scurve_lwd <- ggplot(error_rm_scurve, 
                     aes(x = mean_counts, 
                         y = MSE)) + 
  geom_point(
    size = 1
    ) +
  geom_line(
    linewidth = 0.3
    ) + 
  # geom_vline(xintercept = benchmark1, linetype="solid", 
  #            color = "#bdbdbd", linewidth=1, alpha = 0.5) +
  # scale_x_continuous("standardized bin count", 
  #        transform = "reverse") + 
  scale_x_continuous(breaks = unique(error_rm_scurve$mean_counts)) +
  xlab(expression(mean(n[h]))) +
  ylab("MSE") +
  ggtitle("(c)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

@@

distance_hist <- ggplot(
  distance_scurve, aes(x = distance)) +
    geom_histogram(
      aes(y = after_stat(count) / sum(after_stat(count))), 
      binwidth = bin_width) +
  scale_x_continuous(breaks = bin_labels, labels = round(bin_labels, 2)) +
  ylab("standardized number of edges") +
  xlab(expression(d^{(2)})) +
  ggtitle("(d)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        panel.grid.major.x = element_blank(),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())
